---
title: "Swirl.Summary"
author: "Sihan Wang"
date: "9/29/2018"
output:
  word_document: default
  html_document: default
---
leave the lesson by typing play() and then return by typing nxt()

1.2 Workspace and Files

Get working directory
```{r}
getwd()
```

Create a directory (Add file -in the current working directory)
```{r}
dir.create("testdir")
```

Set working directory
```{r}
setwd("testdir")
```

Create file
```{r}
file.create("mytest.R")
```

Listing file
```{r}
list.files()
```

Check exist
```{r}
file.exists("mytest.R")
```

File info
```{r}
file.info("mytest2.R")
```

Change name
```{r}
file.rename( "mytest.R" , "mytest2.R")
```

Copy
```{r}
file.copy("mytest2.R", "mytest3.R")
```

Path to the file
```{r}
file.path("mytest3.R")
```

Subdirectory
```{r}
file.path('testdir2', 'testdir3')
```

1.3 Vectors

logical expressions
or : |
and : &
negation : !

space : collapse; sep
```{r}
paste(my_char, collapse = " ")
paste("Hello", "world!", sep = " ")
```

recycling : rep()
```{r}
nth = paste0(1:12, c("st", "nd", "rd", rep("th", 9)))
nth
```

1.4 Missing Values (NA)

random : sample()
NA: is.na()
NaN - not a number
equality : ==

1.5: Subsetting Vectors

logical vector -- to extract all elements of a vector that are not NA 
```{r}
x[is.na(x)]
y <- x[!is.na(x)]
x[!is.na(x) & x > 0]
```
subset element
```{r}
x[c(3, 5, 7)] #subset the 3rd, 5th, and 7th elements of x
```
all...except...
```{r}
x[c(-2, -10)]
x[-c(2, 10)]
```
name vector : names()
add names:
```{r}
names(vect2) <- c("foo", "bar", "norf") #add the `names` attribute to vect2 
```
check if same: identical()
specify a vector of names
```{r}
vect[c("foo", "bar")]
```

1.6: Logic

& : and, both true
&& : only first one true
| : or, either true
|| : only first one true

take one argument
```{r}
isTRUE(6 > 4)
isFALSE()
```
takes two arguments : xor()
```{r}
xor(5 == 6, !FALSE)
```

which() : which indices are TRUE
any() : one is TRUE
all() : all is TRUE

1.7 Dates and Times

Sys.time() : current time
Sys.Date() : current date
class() : Object Classes 
```{r}
class(d1)
```
unclass() : internal look
```{r}
 unclass(d1)
```
as.Date() : set a date

dates--'Date' class
times :
  'POSIXct'--> Sys.time()
  'POSIXlt'--> as.POSIXlt(Sys.time()) # list of values

str() : compact view
```{r}
str(unclass(t2))
```
weekdays()
months()
quarters()

strptime() : converts character vectors to 'POSIXlt'
```{r}
strptime(t3, "%B %d, %Y %H:%M") 
```
difftime() : time difference
```{r}
Sys.time() - t1
difftime(Sys.time(), t1, units = 'days')
```

1.8 Function









































